A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-23 doc/paper.tex
User study stuff. Fixes #110, fixes #112

	The participants were most vocal about their findings when they discovered, by
	purpose or accident, instances of heinous design in the dataset. Many times,
	they noted these examples shortly after opening a new tree, suggesting that the
	distinctive visual signatures as discussed in section \ref{badsmells} was a
	salient force in their exploration. For example, when P3 encountered the
	initial design of the SUM tree, as seen in figure \ref{fig:sum}, they readily
	diagnosed that either a spreadsheet author was "totally incompetent, or [the
	formula was] just some that's weird." Other than these visual cues, value
	errors, prefixed with \#s, also appear in the tree where they are found, 
	which P4 said could be useful for tracking these problems if marked well.

@@

	\subsection{Use in Education}
	The inclusion of formula examples, grounded in
	and linking back to the originating spreadsheets, proved to be an especial draw
	to the tool. After all, none of the participants professed themselves to be
	experts with Excel, their self-reported proficiencies ranging from "fairly
	familiar" (P2) to "not extremely familiar" (P4); even if they were experts, it
	would likely be unreasonable to expect an evenly distributed familiarity with
	the 100+ function trees available. Nevertheless, the list of actual formulae
	accessible through a node's double-click allowed the users a way to find
	examples of formulae with exactly the configuration they wanted. For example,
	as P1 explored the VLOOKUP function, even though they knew the official API
	more verbosely explained its signature, they said they could use the tool to
	collect more examples than the documentation offers. \par

	Furthermore, it offers a simple way of finding examples where certain functions
	were used together. though a standard text-search tool might yield the same
	results for a function alone, combinations can require more complex text
	queries, whereas here, the information is already captured in nodes. [This
	paragraph contrasts it with previous approaches, but lacks compelling evidence
	-- a lot of "mights"] \par

	Furthermore, just because a user can exhaustively explore every variation of
	how a function was used doesn't mean they will learn exactly what it does. P1,
	in their exploration, examined functions that they hadn't used before, such as
	KURT and PV, and described precisely what types of arguments it accepted and
	how many. However, even after exploring the spreadsheets, they could not
	accurately describe what the functions produced without consulting the official
	documentation. Whether through reticence of the tool or obscurity of the
	functions themselves, the exploratory environment is not enough for independent
	education. However, unlike the previous problem, this can be addressed,
	perhaps, by guiding the user directly to such documentation from within the
	tool without violating any design concerns. \par

>>>>

	The participants were most vocal about their findings when they discovered, by
	purpose or accident, instances of heinous design in the dataset. Many times,
	they noted these examples shortly after opening a new tree, suggesting that the
	distinctive visual signatures as discussed in section \ref{badsmells} was a
	salient force in their exploration. For example, when P3 encountered the
	initial design of the SUM tree, as seen in figure \ref{fig:sum}, they readily
	diagnosed that either a spreadsheet author was "totally incompetent, or [the
	formula was] just some that's weird." Other than these visual cues, value
	errors, prefixed with \#s, also appear in the tree, 
	which P4 said could be useful for tracking these problems if marked well.

@@

	\subsection{Use in Education} Users found \toolname's inclusion of examples
	to be especially useful since none of the them considered themselves to be
	experts of Excel, their self-reported proficiencies ranging from "fairly
	familiar" (P2) to "not extremely familiar" (P4). For example, as P1 explored
	the VLOOKUP function, they said they could use the tool to collect more
	examples than the documentation offers even though they knew the documentation more verbosely
	explained its function signature. Furthermore, in the process of exploring trees,
	P1 and P3 also gravitated towards some functions they had not used before, such as
	PV and IPMT, looking for new features in Excel to explore and learn. \par

	Additionally, \toolname offers a simple way of finding examples where certain functions
	were used together. Though a standard text-search tool might yield the same
	results for a function alone, combinations can require more complex text
	queries, whereas here, the information is already captured in nodes.  \par

	However, we found that even though a user can explore all of a function's configurations, this
	does not mean that they will learn exactly what it does. P1,
	examining unfamiliar functions like
	KURT and PV, could describe precisely what types of arguments it accepted and
	how many. But even after exploring the spreadsheets for context, they could not
	accurately describe what the functions produced without consulting the official
	documentation. Whether through reticence of the tool or obscurity of the
	functions themselves, the exploratory environment is not enough to teach users
	\textit{when} to use a function. However, we could address this in future designs,
	perhaps, by linking directly to such documentation from within the
	tool without violating any design concerns in \ref{goals}. \par
